Contention management for Cloud Ran over an optical ring

### 2018-02-14 Papier NGreen/article.tex
encore un peu

\todo{ça marque et dans le titre, ça ne devrait pas}

@@

   The antenna are linked to the nodes of the ring through an electronic interface of rate $D$Bps.
   The ring has a rate of $KD$Bps. $K$ is called the {\bf acceleration factor} between the electronic and the optical domains. A node aggregates the data received on the electronic interface during a time $Z/D$ to create a PDU, which fills a container in $Z/KD$s. In other words, the node transforms the data received during a time $Z/D$, called {\bf macro-slot}, into a PDU that can be sent in a slot. Consequently, a single electronic interface can not emit more than one PDU every $k$ slots on the ring.

   To refine our model, one must consider the opto-electronic nodes behaviour.
   Each node of the ring is connected to some external networks by at least one electronic interface of rate $D$Bps. The ring has a rate of $KD$Bps. $K$ is called the {\bf acceleration factor} between the electronic and the optical domains. A node is able to aggregate the data received on the electronic interface during $Z/D$s to create a PDU, which fills a container in $Z/KD$s. In other words, the node transforms the datas received during a time $Z/D$, called {\bf macro-slot}, into a PDU that can be sent in a slot. Consequently, a single electronic interface can not emit more than one PDU every $k$ slots on the ring.

@@

      \includegraphics[scale=0.3]{slot1.pdf}
  \includegraphics[scale=0.3]{slot2.pdf}
     \caption{Opto-electronic interface.}

\end{center}
  \end{figure}

      An node deals with two kinds of traffics. Some C-RAN and some Best Effort. We assume that each traffic has its corresponding electronic interface. Also, a C-RAN message is of size $Z$ and completely fills a container let us call {\bf C-RAN PDU} such a message. In the same time, the Best Effort messages are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}. Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.  
      \begin{figure}[h!]
\begin{center}   
  \includegraphics[scale=0.7]{buffers.pdf}
     \caption{An N-GREEN station.}

\end{center}
  \end{figure}

@@

\subsection{Into the node : Two kind of traffics}

\paragraph{BE PDU generation model} To Generate the BE PDU, we used the distribution of the time between the generation of two BE PDU given by some numerical analysis work of another study for N-GREEN. This distribution was calculated by modelling a gathering buffer.

>>>>

\todo{ça marque et dans le titre, ça ne devrait pas

Il faut citer l'ANR NGREEN + n'importe quel truc de charoni qui explique leur architecture NGREEN}

@@

   The antenna are linked to the nodes of the ring through an electronic interface of rate $D$Bps.
   The ring has a larger rate of $KD$Bps. The integer $K$ is called the {\bf acceleration factor} between the electronic and the optical domains. A node aggregates the data received on the electronic interface during $K$ unit of times to create a PDU of size $Z$, that is which can fills one container of the ring. As a consequence, we consider that each period, an antenna emits a PDU of size $Z$ each $K$ unit of times during a time $ET$.

@@

      \includegraphics[scale=0.2]{slot1.pdf}
  \includegraphics[scale=0.2]{slot2.pdf}
     \caption{Opto-electronic interface.}

\end{center}
  \end{figure}
  \todo{Améliorer le dessin: un seul schéma avec les notations et horizontal pour pas perdre de place.
  Éventuellement faire une représentation du ring et en zoom faire l'interface}
%   
%       An node deals with two kinds of traffics. Some C-RAN and some Best Effort. We assume that each traffic has its corresponding electronic interface. Also, a C-RAN message is of size $Z$ and completely fills a container let us call {\bf C-RAN PDU} such a message. In the same time, the Best Effort messages are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}. Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.  
%       \begin{figure}[h!]
% \begin{center}   
%   \includegraphics[scale=0.7]{buffers.pdf}
%      \caption{An N-GREEN station.}
%      
% \end{center}
%   \end{figure}
%

@@

% 
% 
% \subsection{Into the node : Two kind of traffics}

\todo{Décrire ici les degrés de liberté -> quand ça part + la latence}

\subsection{Best effort traffic}

\todo{Décrire la génération du best effort}

\paragraph{BE PDU generation model} To Generate the BE PDU, we used the distribution of the time between the generation of two BE PDU given by some numerical analysis work of another study for N-GREEN. This distribution was calculated by modeling a gathering buffer.
